Datasheet for Project Gutenberg's 'Stream of Consciousness Literature

### 2024-04-25 paper/datasheet_project_gutenberg.qmd
final datasheet updates

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- No preprocessing/cleaning/labeling on the data was done by Project Gutenbeg.
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- N/A
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- N/A
No, it is unclear what software was used to preprocess, clean, and label the data.
4. *Any other comments?*
	- N/A

>>>>

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- No preprocessing/cleaning/labeling on the data was done by Project Gutenbeg as all archived texts are digitized versions of printed books. They are not new editions.
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- N/A
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- N/A
No, it is unclear what software was used to preprocess, clean, and label the data.
4. *Any other comments?*
	- N/A
